Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-16 Response to reviewers.tex

\begin{verbatim}
The paper describes an ongoing European FP7 research project,
MUSES. It mainly covers the concept behind MUSES, the description of
the architecture, and a high level description of the soft computing
methods to be used, as no actual results have been obtained so far.

A comparison to existing commercial applications is also included, but
this seems taken from their commercial brochures; it does not offer
any clues on how they differ from the functionality offered by MUSES.
\end{verbatim}

The reviewer is right, the state of the art in commercial solutions was quite brief and descriptive.
We have addressed this issue on the revised version of the paper,
changing several sections in order to compose a State of the art in
applications similar to MUSES, and going deeper in the features that
can be compared with those of our system.

We have also compared this solutions with the current features of the
MUSES prototype, which is already being used in tests, in Section 5.

@@

\begin{verbatim}
It is also unclear how this paper differs from previous work by the
same authors (and others), which also aimed to describe the system;
more specifically: 
"Enforcing corporate security policies via computational intelligence
techniques", GECCO Comp '14 Proceedings of the 2014 conference
companion on Genetic and evolutionary computation Pages 1245-1252  
\end{verbatim}

The paper has been improved in a number of ways, making it more
distant with respect to our previous works. Moreover, we have remarked
in the introduction the contributions of the present work with
respect to the previous ones, and included also references to other
research whose result has been included in Muses, for instance:

[10] A. Mora, P. De las Cuevas, J. Merelo, Going a step beyond the black and
white lists for url accesses in the enterprise by means of categorical classi-
fiers, in: A. Rosa, J. J. Merelo, J. Filipe (Eds.), ECTA 2014 - Proceedings
of the International Conference on Evolutionary Computation Theory and
Applications, 2014, pp. 125–134.

@@

\begin{verbatim}
In this reviewer's opinion, the authors should wait till they have
results to present. 
\end{verbatim}

Although in this version of the paper we make reference to the release
of the first versions of MUSES, the main objective  of this paper is
to present a state of the art in BYOD and how the issues present in
this area are addressed using computational intelligence techniques.

@@

\begin{verbatim}
The relationship between the scope of the special issue and the
subjects dealt by MUSES is also unclear
\end{verbatim}

Security and privacy are obviously the main concerns of MUSES: data
security and user privacy. The BYOD philosophy tries to maintain data
security while keeping the privacy of the user's own data and
applications, so we think that the current version of the paper are in
scope of the special issue. The new introduction tries to make this
clearer.

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Addressing more reviewer comments, but some remain to be done by @amorag and @unintendedbear
Re-writing abstract trying to include the structure problem->solution->did we solve it?

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Enterprises, and particularly their Chief Security Officers (CSOs),
want to ensure that their Security Policies are complied, but this
goal turned hard to achieve since employees are able to use, or bring
their own devices (in what is known as BYOD, bring your own device) at
work, or at home but for work purposes. As this BYOD philosophy is
adopted by many companies everyday, a number of solutions have arisen
in order to adopt it securely. In this paper, a novel system named
MUSES (Multiplatform Usable Endpoint Security) which should be able 
to adapt Security Policies to a BYOD environment is introduced. MUSES
has been designed to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules. MUSES applies machine learning and computational intelligence techniques in order to do this, and also would be able to predict future security incidences produced by these users.
This system, which has released its first prototypes this year, is compared with the most relevant
solutions offered by other companies to deal with the same issues as
MUSES, remarking the advantages that our system will offer with
respect to them. % What do we do in this paper? Present the
                 % architecture? The prototypes? - JJ
\end{abstract}

>>>>

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Enterprises, and particularly their Chief Security Officers (CSOs),
want to ensure that their Security Policies are complied, but this
goal turned hard to achieve since employees are able to use, or bring,
their personal devices at work. This has been named as ``Bring Your Own Device'' (BYOD). % <- Problem
As this BYOD philosophy is being adopted by many companies everyday, a number of solutions have appeared in the market, 
in order to adapt to it in a secure way. In this paper, a novel and open source system named
MUSES (Multiplatform Usable Endpoint Security), able 
to securely manage BYOD environments, is described. % <- Solution
MUSES has been developed to cope with security issues with regard to enterprise security policies, but as a user-centric tool. It considers users' behaviour in order to adapt, improve, or even increase the defined set of security rules. To do this, the system applies Machine Learning and Computational Intelligence techniques, being also able to predict future security incidences produced by these users. % <- Solution, details.
MUSES, which has released its first prototype this year, is compared with the most relevant
solutions offered by other companies to deal with the same issues as, remarking the advantages that our system will offer with
respect to them. % <- we will explain why is better in the work

% What do we do in this paper? Present the
                 % architecture? The prototypes? - JJ
\end{abstract}
